Towards typed repositories of proofs

### 2010-06-18 papers/MIPS2010/abstract.tex
* Adresse.
git-svn-id: http://gasp.dev.regis-gianas.com/svn/trunk@129 403e655e-980a-47bd-8c60-1ee5348bb6b7

\author{
\begin{tabular}{cc}
Matthias Puech &
Yann Régis-Gianas \\ 
&
{\small \url{yrg@pps.jussieu.fr}}\\
& 
{\small Laboratoire PPS, équipe ${\pi}r^2$} \\
&
{\small University Paris 7, CNRS, and INRIA}
\end{tabular}
}
\date{}

>>>>

\author{
\begin{tabular}{cc}
Matthias Puech &
Yann Régis-Gianas \\ 
&
{\small \url{yrg@pps.jussieu.fr}}\\
& 
{\small Laboratoire PPS, équipe ${\pi}r^2$} \\
&
{\small University Paris 7, CNRS, and INRIA} \\
&
{\small 23, avenue d'Italie. 75013 Paris}
\end{tabular}
}
\date{}
